Enabling the Use of GPU Virtualization in Cloud Environments

### 2015-10-08 paper.tex

For this study, the instances presented in the Table~\ref{table:awsInstances} 
have been selected. The C3 family instances, which are not equipped with 
GPUs are going to be used as client whereas the instances of the G2 family are 
acting as servers.

@@

The IPERF tool has been executed between the instances showed in 
the Table~\ref{table:iperf} in order to know the real bandwidth.
Therefore, we can assure that the nomenclature ``High'' used in the 
network column correspond to a 1~Gb interconnection and the 10~Gb has 
a real bandwidth of 7.5~Gb/s.
Moreover, it looks like the instances equipped with a ``High'' interconnection 
are software-limited up to 1~Gb/s due to the theoretical and real bandwidth 
match perfectly. The gap between real and theoretical can be observed with 
the 10~Gb interconnection which reaches up to 7.5~Gb/s.

\subsubsection{GPUs}
As it has been said before, an instance is based in a VM 
which is running on a real node with its own virtualized 
components, so it is possible that AWS could use a virtualization 
framework to offer GPU services to all the instances.
Therefore, we need to verify if the GPUs showed in the instances are 
non-virtualized GPUs so, we have executed the NVIDIA SDK test called 
{\tt bandwidthtest}. As it is shown in the Table~\ref{table:bwt}, as the bandwidth achieved 
in this test is higher than the network bandwidth, it reveals that it is a 
real GPU. 
\begin{table}[htb]
\renewcommand{\arraystretch}{1.3}
\caption{NVIDIA SDK {\tt bandwidthtest} execution transferring 32MB using pageable memory using local GPU.}
\label{table:bwt}
\tabcolsep=0.09cm
\begin{center}\begin{tabular}{cccc}
Name &  Data Movement & Network & Bandwidth \\ \hline \hline
g2.2xlarge & Host to Device & High& 3,004 MB/s \\ \hline
g2.2xlarge & Device to Host & High& 2,809 MB/s\\ \hline
g2.8xlarge & Host to Device & 10 Gb& 2,814 MB/s\\ \hline
g2.8xlarge & Device to Host & 10 Gb& 3,182 MB/s\\ \hline
\end{tabular}\end{center}\end{table}

>>>>

For this study, carried out in June 2015, we worked in the AWS availability zone US EAST (N. VIRGINIA). 
So, at this moment the instances used had the features presented in the Table~\ref{table:awsInstances}.

@@

The IPERF\footnote{\url{http://iperf.fr/}} tool has been executed between the instances showed in 
the Table~\ref{table:iperf} in order to know the real bandwidth.
Therefore, we can assure that the nomenclature ``High'' used in the 
network column correspond to a 1~Gb interconnection and the 10~Gb has 
a real bandwidth of 7.5~Gb/s.
Moreover, it looks like the instances equipped with a ``High'' interconnection 
are software-limited up to 1~Gb/s due to the theoretical and real bandwidth 
match perfectly. The gap between real and theoretical can be observed with 
the 10~Gb interconnection which reaches up to 7.5~Gb/s.

\subsubsection{GPUs}
As it has been said before, an instance is based in a VM which is running on a real node with its own virtualized components, so it is possible that AWS could use a virtualization framework to offer GPU services to all the instances.
Although, the {\tt nvidia-smi} command informs us that the GPUs installed are NVIDIA GRID K520, we need to verify that they are non-virtualized devices so, we have executed the NVIDIA SDK test called {\tt bandwidthtest}. 
As it is shown in the Table~\ref{table:bwt}, as the bandwidth achieved in this test is higher than the network bandwith, it reveals that it is a real GPU. 
\begin{table}[htb]
\renewcommand{\arraystretch}{1.3}
\caption{NVIDIA SDK {\tt bandwidthtest} execution transferring 32MB using pageable memory using local GPU.}
\label{table:bwt}
\tabcolsep=0.09cm
\begin{center}\begin{tabular}{cccc}
Name &  Data Movement & Network & Bandwidth \\ \hline \hline
g2.2xlarge & Host to Device & High& 3,004 MB/s \\ \hline
g2.2xlarge & Device to Host & High& 2,809 MB/s\\ \hline
g2.8xlarge & Host to Device & 10 Gb& 2,814 MB/s\\ \hline
g2.8xlarge & Device to Host & 10 Gb& 3,182 MB/s\\ \hline
\end{tabular}\end{center}\end{table}
